---
title: "Flash Floods, Business Adjustment, and Ripple Effects on Displaced Workers"
subtitle: "Replication Package"
author:
  - "Pedro Jorge Alves"
  - "Philipp Ehrl"
  - "Ricardo C. A. Lima"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: show
params:
  run_main: false
  run_appendix: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = TRUE,
  warning = TRUE,
  error = FALSE
)

project_root <- normalizePath(
  dirname(knitr::current_input(dir = TRUE)),
  winslash = "/",
  mustWork = TRUE
)
knitr::opts_knit$set(root.dir = project_root)
```

# Overview

This is the main executable document for the replication package of
*Flash Floods, Business Adjustment, and Ripple Effects on Displaced Workers*.
It provides a single entry point for reproducing the results while keeping
the exhibit-specific scripts organized under `results/code`.

The establishment-level treatment group contains firms located within 5 km
of the mapped flood spots. The baseline control group contains firms located
between 50 and 80 km from those spots.

The synthetic aperture radar (SAR) data used in this project were made
available by Marinho and were collected and processed as described in
\cite{marinho2012aplicaccao}. They identify the precise location and spatial
extent of the areas flooded in 2008. According to this mapping, the disaster
generated more than 1,022 flooded spots covering a total area of 7,452
hectares. The source layers
combine flood classifications derived from TerraSAR-X, RADARSAT-2 (ascending
and descending passes), and ENVISAT ASAR radar imagery into a single polygon
layer. Because radar can detect inundation despite cloud cover, these data
provide a detailed representation of the disaster footprint. Distances from
establishments to the mapped flood extent are then used to define the
treatment and control rings.

## From the national RAIS files to the analytical panels

The restricted microdata used in the analysis originate in the annual,
nationwide files of the Relação Anual de Informações Sociais (RAIS). The raw
RAIS records are first standardized across years, and the confidential
establishment and worker identifiers are used to link observations over
time. Establishment addresses are geocoded and spatially joined to the 2008
SAR flood map. For every establishment, we calculate the distance from its
pre-disaster 2007 location to the nearest mapped flooded area.

The geographic restriction is imposed using the 2007 baseline, before the
disaster and before outcomes are followed:
establishments located no more than 5 km from a mapped flooded area form the
treatment area, while establishments located between 50 and 80 km form the
baseline control area. Establishments in the intervening 5--50 km band or
beyond 80 km are not part of the baseline comparison. Once this baseline
sample and treatment status have been defined, the confidential identifiers
are used to recover the same establishments from the annual RAIS files and
track them backward and forward over time. Thus, later outcomes do not cause
an establishment to enter the treatment or control area; the spatial groups
are anchored to the pre-disaster location. Outcomes remain observed after a
unit relocates, including when its later location falls outside the original
distance bands. The main establishment panel covers 2003--2012, and the
extended analysis follows establishments through 2016.

The worker panel is constructed from the linked employment records of these
establishments. The baseline worker sample retains workers employed at the
same establishment in 2006 and 2007 and follows their subsequent employment,
earnings, and location in RAIS. Most worker analyses cover 2003--2012, while
the extended specifications continue through 2016. These processing steps
were carried out in the authorized secure environment; the repository begins
with the resulting restricted analytical files because neither the national
RAIS microdata nor the intermediate identified crosswalks can be released.

# Directory structure

```text
flashfloods-sc-project/
├── Main_analysis.Rmd
├── README.md
├── data/
└── results/
    ├── code/
    │   ├── Main Estimates/
    │   ├── Appendix/
    │   └── utils/
    └── analysis/
```

- `data` is the expected local location of the restricted input databases;
  these files are not distributed with the repository.
- `results/code` contains the version-controlled main, appendix, and shared R
  scripts.
- `results/analysis` receives locally generated figures and tables.

The directory tree records the expected replication workflow. The restricted
inputs and generated outputs do not need to be included in a code-only
distribution.

# Reproduction controls

The document does not run the estimations when knitted with the default
parameters. This prevents an accidental full replication, which can be
computationally intensive.

To reproduce the main results, render with:

```r
rmarkdown::render(
  "Main_analysis.Rmd",
  params = list(run_main = TRUE, run_appendix = FALSE)
)
```

To reproduce everything, use:

```r
rmarkdown::render(
  "Main_analysis.Rmd",
  params = list(run_main = TRUE, run_appendix = TRUE)
)
```

# Main results

The main runner executes the exhibits in the order in which they appear in
the paper and saves their outputs in `results/analysis`.

```{r run-main-results}
if (isTRUE(params$run_main)) {
  source(file.path(project_root, "results", "code", "run_main_estimates.R"))
} else {
  message("Main estimations skipped. Set params$run_main = TRUE to run them.")
}
```

# Appendix results

The appendix runner executes the municipal balance analysis, distance-band
analysis, establishment robustness exercises, worker results, and HonestDiD
sensitivity analysis.

```{r run-appendix-results}
if (isTRUE(params$run_appendix)) {
  source(file.path(project_root, "results", "code", "run_appendix.R"))
} else {
  message("Appendix estimations skipped. Set params$run_appendix = TRUE to run them.")
}
```

# Code and corresponding results

## Main text

| Exhibit | Script |
|:--|:--|
| Figure 1 — Geographical Distribution | `Main Estimates/01_figure1_geographical_distribution_affected_area.R` |
| Table 1 — Summary Statistics | `Main Estimates/01_table1_summary_statistics.R` |
| Figure 2 — Aggregate Outcomes | `Main Estimates/02_figure2_evolution_aggregate_outcomes.R` |
| Table 2 — Establishment Adjustment | `Main Estimates/03_table2_establishment_adjustment.R` |
| Figure 4 — Establishment Event Study | `Main Estimates/04_figure4_event_study_establishments.R` |
| Tables 3–5 | `Main Estimates/05_...R` through `07_...R` |
| Table 6 — Dismissed Workers | `Main Estimates/08_table6_dismissed_workers.R` |
| Figure 5 — Worker Event Study | `Main Estimates/09_figure5_event_study_workers.R` |

## Appendix

| Section | Code folder |
|:--|:--|
| A | `Appendix/A_Municipal_Balance` |
| B | `Appendix/B_Distance_Band_Analysis` |
| C | `Appendix/C_Establishment_Robustness` |
| E | `Appendix/E_Workers_Balancing` |
| F | `Appendix/F_Exposed_Workers` |
| G | `Appendix/G_Worker_Robustness` |
| H | `Appendix/H_Robust_Confidence_Intervals` |

# Session information

```{r session-information}
sessionInfo()
```

# Data availability and confidentiality

The data used in this project are not publicly available and are not
distributed with this replication package. They contain sensitive,
identifiable, or potentially identifiable information on firms and workers
and must be handled in accordance with Brazil's General Data Protection Law
(Lei Geral de Proteção de Dados Pessoais — LGPD, Law No. 13,709/2018) and the
applicable confidentiality agreements.

Access to the restricted microdata must be requested directly from the
responsible data custodians and is subject to their authorization,
confidentiality requirements, and secure-use procedures. The replication
package therefore provides the code and documentation, but not the underlying
restricted databases. In particular, the nationwide RAIS files, geocoded
establishment addresses, longitudinal identifier crosswalks, and the derived
establishment and worker panels cannot be redistributed.

The SAR imagery and derived 2008 flood polygons used to construct distance to
the disaster were made available by Marinho and are documented in
\cite{marinho2012aplicaccao}. They are not included in this public package;
access or redistribution requires authorization from the relevant data
provider. The code therefore expects the authorized user to place both the
restricted RAIS-derived files and the flood layer in the local `data`
directory.
